My title

### 2024-02-18 outputs/paper/paper.qmd
updated file organization

sum_table_wide <-
  read_csv(
    file = "../data/analysis_data/sum_table_wide.csv",
    show_col_types = FALSE
  )

@@

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: fig-foodChoices
#| fig-cap: "Students food choices from stage G1 to G2 comparing grape to cookie, cookie to grape, or no change."

public_data <-
  read_csv(
    file = "../data/analysis_data/public_data.csv",
    show_col_types = FALSE
  )

@@

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: fig-lunchStatus
#| fig-cap: "Comparing incentivized students choosing grapes if they are eligible or not eligable for the free lunch program"

@@

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: fig-grade
#| fig-cap: "Comparing incentivized students choosing grapes or cookies by the students grade"

@@

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: fig-gender
#| fig-cap: "Comparing incentivized students choosing grapes or cookies by the students gender"

>>>>

sum_table_wide <-
  read_csv(
    file = "../data/sum_table_wide.csv",
    show_col_types = FALSE
  )

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-foodChoices
#| fig-cap: ": Students food choices from stage G1 to G2 comparing grape to cookie, cookie to grape, or no change."

public_data <-
  read_csv(
    file = "../data/public_data.csv",
    show_col_types = FALSE
  )

@@

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: fig-lunchStatus
#| fig-cap: ": Comparing incentivized students choosing grapes if they are eligible or not eligable for the free lunch program"

@@

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: fig-grade
#| fig-cap: ": Comparing incentivized students choosing grapes or cookies by the students grade"

@@

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: fig-gender
#| fig-cap: ": Comparing incentivized students choosing grapes or cookies by the students gender"
